Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2017-03-27 paper.tex
Added description of book categories
But there are multiple grammar edits, too. Grammar has to be revised
_very_ extensively before it is submitted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining the number 
of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
The obtained results will be easier to interpret by publishers than other black-box techniques, 
so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.

The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
% Antonio - explain briefly what are them  and  the followed methodology.
In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
% Explain also the method you are using and why it's an improvement over the previous one - JJ
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

\begin{keyword}
% Antonio - to refine later
Book sales forecasting \sep Decision-aid models \sep Feature selection \sep Classification \sep Ensemble methods
\end{keyword}

@@

Moreover, handling the problem as a classification task let us to emphasize on the ranges which could be more `critical', e.g. the most profitable books (High and Very High categories). Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
% which will be definitely very interesting for publishers.

@@

In this line, the most used techniques to tackle sales forecasting problems have been time-series prediction
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
Moreover, this kind of methods are based on using historical data about an article to make time series. However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data for that product \cite{ChingChin2010}, and only pre-sales data can be considered \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale.

@@

In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
to forecast the future sales of a printed circuit board is proposed.
% Antonio - compare it with our work
Recent works propose to take advantage of the information extracted from online reviews, such as in \cite{ChernWSF15} where it is conducted an analysis on historical data throughout online reviews, reviewer characteristics, and review influences; in order to understand how electronic `word-of-mouth' influences product sales.
Similar researches took advantage of the information published on specialized 
blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, confirming there is a relationship between the number of blog references and the book sales. Therefore, different sales patterns have been observed by analysing books in series, i.e. the first book published takes the longest period to achieve every single sales scale, while the second book takes the second longest period, and so on.
In these cases, sales forecasting problems can be carried out thanks to a big 
amount of online reviews and historical data.
% Antonio - compare these works and findings with our current work

@@

The obtained dataset contains collected information about 6083 different books produced by 209 publishers. Each book or pattern in the dataset is represented by 10 features as shown in Table \ref{tabla:params_pre_sales}.

\begin{table*}
\caption{Pre-sales features and Sales level(Output class). } 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 & bookbinding (code) & \texttt{binding} & categorical & input\\
4 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
5 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
6 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
7 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
8 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
9 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
10 & Sales level & \texttt{sales\_level} & categorical & output\\
\hline 
\end{tabular}
\end{center}
\end{table*}

The output variable which is related to the total amount of sales is a categorical variable which represent the level of the quantity sold for a given book. Thus, four categories have been considered to represent these levels: \textit{Low (L)}, \textit{Medium (M)}, \textit{High (H)}, and \textit{Very High (VH)}. Table \ref{table:freq} shows the ranges of total sales that correspond to each category along with the number of sold books that fall in. The discretization of the volume of sales was conducted by an expert in the domain of editorial management business, who defined the four categories.
% Antonio - TODO: It would be great if we could justify... At least, the expert (JJ :P) could write a sentence clarifying his decision for these ranges.

Table \ref{table:freq} reveal more information about the nature of the dataset. We can notice that most of the investigated books are categorized as Low and Medium levels forming 26.8\% and 36.4\% of the dataset, respectively. High volumes of sold books that range from 301 up to 1000 are categorized as High volume of sales and form 24\% of the dataset. On the other hand, books that achieved more than 1000 sold copies are categorized as Very High and they form around 12.8\% of the dataset. Our focus in this study is to identify the more profitable categories which are High and Very High. However, since the latter category is much smaller than the other ones, we can describe our dataset as imbalanced dataset which makes the problem of identifying this category harder and more challenging.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
%First you have to explain why it is enough to predict the level of
%sales, and not the precise number. 
% Antonio - it is true, but how can we justify this, JJ?
% I guess that precision is relative in this kind of methods, since the publisher is not going to print exactly '237' books due to it is the output of a regression method. Instead, there could be a range of books to be printed (as a standard) related with an expected 'low', 'medium', 'high' or 'very high' amount of sales.
% Moreover, I guess that the classification output, considering four classes would work better (more precisely and close to reality) than regression.
% What do you think?
An important task when publishing a new book is determining the number 
of copies to be printed, since doing both a (dramatic) under- or overestimation will lead to important financial losses.
In this paper, we transform this problem into a classification one, defining different sales levels i.e. classes. 
The obtained results will be easier to interpret by publishers than other black-box techniques, 
so these methods can be used as reliable decision-aid tools for publishers, to be considered in their decision as a part of the final stages of the editorial process.
% paragraphs in the abstract is not a good idea.
The problem of predicting these levels has been addressed applying cost-sensitive ensemble methods.
% Antonio - explain briefly what are them  and  the followed methodology.
In order to do so, a real dataset collected by a Spanish publishing company, including the complete sales data for books published in Spain across several years, has been used to design and evaluate the prediction models.
% Explain also the method you are using and why it's an improvement over the previous one - JJ
Results show that %\emph{EXPLAIN THE RESULTS OBTAINED}.

@@

\begin{keyword}
% Antonio - to refine later
Book sales forecasting \sep Decision-aid models \sep Feature selection
\sep Classification \sep Ensemble methods %why commas _and_ CAPS? - JJ
\end{keyword}

@@

Moreover, handling the problem as a classification task let us to
emphasize on the ranges which could be more `critical', e.g. the most
profitable books (High and Very High categories). % You have used
                                % italics for this before but no
                                % emphasis now. You have to unify
                                % typography - JJ
Thus, we can penalize more the misclassification of these categories and, consequently, this tool will perform a better identification of successful books than our previous approach \cite{Castillo2016books}.
% which will be definitely very interesting for publishers.

@@

In this line of work, the most widely used techniques to tackle sales forecasting problems have been time-series prediction
\cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990}. %,KayacanUK10}. % Antonio - the last reference doesn't exist
However these methods are strongly dependent on problem data, so the obtained predictions are highly affected by their correctness.
Moreover, this kind of methods are based on using historical data about an article to make time series. However, in the case of new products sales prediction (such as the issue of new books), there is no available historical sales data for that product \cite{ChingChin2010}, and only pre-sales data can be considered \cite{FaderHardie2005,Madsen2008}, 
i.e. variables known before the product is on sale.

@@

In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
to forecast the future sales of a printed circuit board is proposed.
% Antonio - compare it with our work
Recent works propose to take advantage of the information extracted from online reviews, such as in \cite{ChernWSF15} where it is conducted an analysis on historical data throughout online reviews, reviewer characteristics, and review influences; in order to understand how electronic `word-of-mouth' influences product sales.
Similar research efforts took advantage of the information published
on specialized  %please revise 
blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, confirming there is a relationship between the number of blog references and the book sales. Therefore, different sales patterns have been observed by analysing books in series, i.e. the first book published takes the longest period to achieve every single sales scale, while the second book takes the second longest period, and so on.
In these cases, sales forecasting problems can be carried out thanks to a big 
amount of online reviews and historical data.
% Antonio - compare these works and findings with our current work

% There is no clear narrative here. State of the art must show the
% progression in this kind of work and how different levels of success
% have been achieved via different methods. You have to hint that what
% we are using here, sales levels, is going to be better than
% predicting sales via a regression model, for instance - JJ

@@

The obtained dataset contains collected information about 6083
different books produced by 209 publishers. Each book or pattern in
the dataset is represented by 10 features, listed in Table
\ref{tabla:params_pre_sales}. 
%
\begin{table*}
\caption{Pre-sales features and Sales level(Output class). } 
\label{tabla:params_pre_sales}
\begin{center}
\begin{tabular}{|c|l|l|c|c|}
\hline 
No. & Feature Name & Variable & Type & In/Out\\
\hline 
1 & retail price (when launched) & \texttt{ret\_price} & numerical & input\\
2 & main subject (code) & \texttt{subject1} & numerical & input\\
3 & bookbinding (code) & \texttt{binding} & categorical & input\\
4 & gifts (promotional books) & \texttt{gifts} & numerical & input\\
5 & units distributed as novelty & \texttt{distrib\_novelty} & numerical & input\\
6 & total number of points of sale & \texttt{tot\_points\_sale} & numerical & input\\
7 & total number of points of sale (1st year) & \texttt{tot\_points\_sale\_1st\_year} & numerical & input\\
8 & weeks on sale & \texttt{weeks\_sale} & numerical & input\\
9 & print run & \texttt{print\_run} & numerical & input\\
\hline 
\hline
10 & Sales level & \texttt{sales\_level} & categorical & output\\
\hline 
\end{tabular}
\end{center}
\end{table*}

The output variable related to the total amount of sales is a
categorical variable which represent the level of the quantity sold
for a given book. We have defined four categories to
represent these levels: \textit{Low (L)}, \textit{Medium (M)},
\textit{High (H)}, and \textit{Very High (VH)}. Table \ref{table:freq}
shows the ranges of total sales that correspond to each category along
with the number of sold books that fall in. The discretization of the
volume of sales was conducted by an expert in the domain of editorial
management business, who defined the four categories. They are also
adapted to the Spanish market. The first level, 60, corresponds to the
first quartile in the book sales distribution: 25\% of books sell less
than 60 copies. The second has been established at the typical print
run in the Spanish market, which is 300 copies, including not only
books for sale, but also books sent as a gift, to display or for
reviewers. 1000 books would be considered a decently selling book with
several print runs; second print run will depend on how fast the first
one sales, but could typically be 500 to 1000 new copies. Anything
selling more than 1000 copies will sell extremely well, with only 60
books reaching more than 5000 physical copies sold in the data set we
used. These sales levels will have to be adjusted to particular
markets using the same methodology we have used here, although a good
rule of thumb would be, after examining the initial data set and the
distribution of sales among different books, to choose the 4 quartiles
or 3 terciles and split the top one giving the ``very high'' category
to the books in the top decile.

Table \ref{table:freq} reveal more information about the nature of the
dataset. Please note that most of the investigated books are
categorized as Low and Medium %once again, unify typography
levels forming 26.8\% and 36.4\% of the dataset, respectively. High
volumes of sold books that range from 301 up to 1000 are categorized
as High volume of sales and form 24\% of the dataset. On the other
hand, books that achieved more than 1000 sold copies are categorized
as Very High and they form around 12.8\% of the dataset. Our focus in
this study is to identify the more profitable categories which are
High and Very High. However, since the latter category is much smaller
than the other ones, we can describe our dataset as imbalanced which
makes the problem of identifying this category harder and more
challenging.
